---
title: "Intro to trafiklabAPI"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro to trafiklabAPI}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo = FALSE, message = FALSE, warning=FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
```

```{r, echo = FALSE, message = FALSE, warning=FALSE}
library(trafiklabAPI)
```

`trafiklabAPI` allows you to search for nearby public transportation stops based on longitude and latitude coordinates through trafiklabAPI. Based on the functions inside this package you can do the following:

* Specify your location in latitude and longitude coordinates and receive information about these stops in terms of names, distance to your location etc.

* Search for names of stops with trafiklab's fuzzy match and receive suggestions for your search along with information about these stops.

To make use of all the awesome features of `trafiklabAPI`-package and functions you'll need a unique (personal) API key, for more information about this key, visit trafiklab's [website](https://www.trafiklab.se/api).


### `nearby_stops`: Searching for locations based on longitude and latitude

Specifying all parameters in the model gives you more control over the output. Below is an example of how to run `nearby_stops` with default values for all parameters, except for `api_key`, which you'll need to apply for yourself!

```{r, echo = TRUE, eval = FALSE, message = FALSE}
# not run:
nearby_stops(longitude     = 16.178, 
             latitude      = 58.591, 
             radius        = 1000,
             api_key       = your_unique_key,
             max_locations = 5L)
```

The function automatically adjusts `radius` outside interval [50, 9999] meters and `max_locations` outside interval [1, 50] stops. 

### `location_lookup`: Searching for stops based on name (fuzzy match) 

For `location_lookup`-function, the names can be misspelled and the function still returns some output. Below is an example how to run the function with four stops using `lapply`.  

```{r, echo = TRUE, eval = FALSE, message = FALSE}
# not run:
stop_fuzzy_names <- c("nobeltorget", "skarphagens c", 
                      "linköping centr", "falla")

# set names to stop_fuzzy_names in order to have named output!
names(stop_fuzzy_names) <- stop_fuzzy_names           

lapply(X             = platser, 
       FUN           = location_lookup, 
       api_key       = your_unique_key,
       max_locations = 5L)
```

`location_lookup` has the same limits regarding `max_locations` as `nearby_stops`.